A Search for Supernova Remnants in NGC\,6946

### 2018-11-19 ms.tex
Updates discussing extinction

Of the 27 SNR candidates identified by MF97, all have imaging [SII]:\ha\ ratios that exceed 0.4. MF97 obtained spectra of six of their candidates.  We have obtained spectra of 23 of the MF97 objects, including new spectra of the 5 objects for which MF97 had spectra. Four -- MF003, MF021, MF022, and MF026 -- were observed spectroscopically.  All of these have measured spectroscopic ratios exceed 0.4.

\todo[inline]{We need a more complete discussion of MF97 and our results.  Possibly this is something wpb could do}

>>>>

Of the 27 SNR candidates identified by MF97, all have imaging [SII]:\ha\ ratios that exceed 0.4. MF97 obtained spectra of six of their candidates.  We have obtained spectra of 23 of the MF97 objects, including new spectra of the 5 objects for which MF97 had spectra. Four -- MF003, MF021, MF022, and MF026 -- were observed spectroscopically.  All of these have measured spectroscopic ratios exceed 0.4.
\todo[inline]{We need a more complete discussion of MF97 and our results.  Possibly this is something wpb could do}

\hb:\ha\ ratios of the SNR candidates with spectra are shown in Fig.\ \ref{fig_reddening} as a function of galacto centric distance. Nearly all of the the SNRs show significant reddening, as one would expect since at 12\degr\ from the Galactic plane, reddening from within the Galaxy along the line of sight to be E(B-V) of 0.29 \citep{schlafly11}.  There is clearly substantial internal reddening as well, and a very evident trend for objects near the center of NGC6946 being more reddened than those that are more distant from the nucleus.
